Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-22 ms.tex
finished caption for f1 figure

\begin{figure}
\begin{center}
\epsfig{file=f1_1deg.eps, width=3.3in}
\caption{\label{fig:f1} $1^{\circ}$ FWHM map of $f_1$ derived from our 
low-resolution fit in which $f_1$ is allowed to vary spatially. Red coloring
masks pixels with appreciable molecular emission, as defined in 
$\S$\ref{sec:mole}. Such pixels should not be trusted in this analysis, which 
is sensitive to the SED shape at low frequencies that are contaminated by CO 
line emission.}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\epsfig{file=f1_1deg.eps, width=3.3in}
\caption{\label{fig:f1} $1^{\circ}$ FWHM map of $f_1$ derived from our 
low-resolution fits described in $\S$\ref{sec:lores}. Red coloring masks pixels
with appreciable molecular emission, as defined in $\S$\ref{sec:mole}. Such 
pixels should not be trusted in this analysis, which is sensitive to the SED 
shape at low frequencies affected by CO line emission. Variations in $f_1$
along the ecliptic plane are spurious results of imperfect zodiacal light
subtractions. However, interesting astrophysical variations of $f_1$ 
are evident, particularly the trend of increasing $f_1$ with decreasing
Galactic latitude, the relatively low $f_1$ values in the Polaris flare region,
and the clouds with relatively high $f_1$ near the north Galactic pole.}
\end{center}
\end{figure}
